---
title: "Homework 3"
author: "Luma Lazarini"
date: "insert date here"
format:
  html:
    toc: true # use this to display a table of contents
execute:
  message: false # use this to make sure messages don't show up
  warning: false # use this to make sure warnings don't show up
---

# 1. Set up

```{r libraries-and-data}
library(tidyverse) # general use
library(janitor) # cleaning data frames
library(here) # file/folder organization
library(ggeffects) # generating model predictions
library(gtsummary) # generating summary tables for models
library(gt)

```

# 1. Personal data

## a. Data Summarizing
I could calculate the mean screen time in minutes to compare my average screen time with the average minutes I spent in class. In days that I spent greater time in class, I would expect to have a lower screen time.

## b. 
```{r}
#reading in my data
screen_time <- read_csv(Users/lumabraconi/Documents/ENVS-193DS/ENVS-193DS_homework-03/data/screen_time.csv)

```
```{r}
#create a category based on class time
data <- data %>%
  mutate(class_time_group = ifelse(`Minutes of class` > median(`Minutes of class`, na.rm = TRUE),
                                   "High Class Time", "Low Class Time"))
  
#creating visualization
ggplot(data= HW 1 ENVS 193DS - Screen time.csv, 
       aes(x = class_time_group, 
           y = `Screen time (min)`, 
           fill = class_time_group)) +
  geom_jitter(width = 0.2, 
              alpha = 0.6, 
              color = "black") +  # individual data points
  stat_summary(fun = mean, 
               geom = "crossbar", 
               width = 0.5,
               color = "darkred", 
               fatten = 2, 
               show.legend = FALSE) +  # mean bars
  scale_fill_manual(values = c("High Class Time" = "#2E86AB", 
                               "Low Class Time" = "#F18F01")) +
  labs(
    title = "Average Screen Time by Class Time Group",
    x = "Class Time Group",
    y = "Screen Time (minutes)"
  ) +
  theme_minimal()
```


# 2.  Affective visualization

## a.
A form of affective data visualization I can use to depict my personal data  would be to draw a student sitting in class, completely glued to their phone, while the teacher is in the background. I’d exaggerate the artwork by having the phone glow or even have the student melting into the screen to show how consuming it is. This would reflect the behavioral side of my data to test whether being in class actually limits my screen time, or if it doesn't change anything. The goal would be to make the viewer feel the disconnect that phones can cause, even in learning environments.
